\documentclass[aip,graphicx,sd, amsmath,amssymb]{revtex4-1}
%\documentclass[aip,reprint]{revtex4-1}

\begin{document}
\section{Basic molecular dynamics}
Text Reference: Frenkel\&Smit, Section 4.1 - 4.3, 6.1.1

Code Reference: ./ExampleCode/tps\_integrator.f90

\begin{enumerate}
\item[\it{i})] \textbf{[Getting an integrator!]} \\
1. Consider a one-dimensional harmonic oscillator (HO),
\begin{align}
H = \frac{p^2}{2m} + V(q), \quad V(q)=\frac12 m \omega^2 q^2
\end{align}
with $m=1$, $\omega=1$. Implement Euler, Verlet, velocity-Verlet integrator and propagate a trajectory $q(t)$, $v=\dot{q}(t)$ starting from a non-trivial initial condition, i.e. $p(0) \neq 0$ or $q(0) \neq 0$. Use $\Delta t=0.001$ for the integration step. Compare numerical result with the analytical one.

2. Plot kinetic, potential and total energy along the trajectories. Check energy conservation along the trajectory by defining
\begin{align}
\bar{E} = \int  dt \hspace{2pt} E(t) \left/ \int dt \right.
\end{align}
and 
\begin{align}
\sigma_E^2 = \int  dt \hspace{2pt} \left| E(t)- \langle E \rangle \right|^2  \left/ \int dt \right.
\end{align}
Compare energy mean and variance from different integrators and time steps.

3. Repeat the calculations for an asymmetrical Morse oscillator (MO)
\begin{align}
V(q) = D_e \left( 1- e^{-a q} \right)^2.
\end{align}
with $a=1$. Choose proper $D_e$ s.t. HO in {\it{i}})-1 is the second-order expansion of MO here. Quantitatively describe the difference between trajectories from two oscillators.

\item[\it{ii})] \textbf{[From NVE to NVT ensemble]} \\
1. (Static quantity) Simulate second moment of position 
\begin{align}
 \langle q^2 \rangle = \int dp dq  \hspace{2pt} e^{-\beta H} \times q^2
\end{align}
of the HO  in {\it{i}})-1 with Andersen thermostat at $\beta=1$. Experimenting the frequency of stochastic collisions in the thermostat to ensure a proper sampling. Compare numerical result with the analytical one.

2. (Static quantity) Sample the distribution . Plot the histogram.

3. (Dynamical quantity)

\end{enumerate}

\end{document}
